%------------------------
% Resume in LaTeX
% Author : Aditya Singh
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc} % Use UTF-8 encoding for broader character support
\usepackage{geometry}
\geometry{margin=1in} % Standard margin size for better readability
\usepackage{url}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}

% Define custom title format
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{4pt}

\begin{document}

% Remove page numbers for resumes
\pagestyle{empty}

% Custom commands for structuring resume content
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------Header--------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Aditya Singh} & \\
  \textit{(Template Version)} & \\
  \href{mailto:adityarathore2606@gmail.com}{adityarathore2606@gmail.com} & \\
  \href{https://github.com/EchoSingh}{GitHub: EchoSingh} & \\
  \href{https://www.linkedin.com/in/adityasinghgdev/}{LinkedIn: adityasinghgdev} & \\
  \href{https://huggingface.co/adi2606}{Hugging Face: adi2606} & \\
\end{tabular*}

%----------Education-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Dayananda Sagar College Of Engineering}{Bengaluru, India}
    {B.E in Information Science (VTU)}{2022 -- 2026}
    \resumeItemListStart
      \resumeItem{Current SGPA: 9.4}
    \resumeItemListEnd
    
  \resumeSubheading
    {Army Public School, Bhopal}{Bhopal, India}
    {Higher Secondary (CBSE)}{2020 -- 2021}
    \resumeItemListStart
      \resumeItem{Percentage: 96.4\% (Class 12th)}
    \resumeItemListEnd
    
  \resumeSubheading
    {Army Public School, Bhopal}{Bhopal, India}
    {Secondary School (CBSE)}{2018 -- 2019}
    \resumeItemListStart
      \resumeItem{Percentage: 90.6\% (Class 10th)}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------Achievements---------
\section{Achievements and Certificates}
\resumeItemListStart
  \resumeItem{Participated in Hack Refine Hackathon (2024). Links: \href{https://github.com/EchoSingh}{GitHub}}
  \resumeItem{Participated in Aventus 2.0 National-level Hackathon (2024). Links: \href{https://github.com/EchoSingh}{GitHub}}
  \resumeItem{Top 10 in Sandbox 2025 Cybersecurity Hackathon (2024). Links: \href{https://github.com/EchoSingh}{GitHub}}
\resumeItemListEnd

%----------Projects------------
\section{Projects}
\begin{tabularx}{\linewidth}{@{}X X@{}}
  \textbf{Math-Wizard} & \textbf{MediBot} \\
  \textit{A mathematical problem solver with step-by-step explanations.} & \textit{A medical chatbot powered by Medical-Llama3-8B for medical queries.} \\
  \textbf{Technologies:} Python, Gradio, Transformers, PyTorch & \textbf{Technologies:} Jupyter Notebook, CUDA, Transformers \\
  \textbf{Links:} \href{https://github.com/EchoSingh/Math-Wizard}{GitHub}, \href{https://huggingface.co/spaces/adi2606/Math_Wizard}{Demo} & \textbf{Links:} \href{https://github.com/EchoSingh/FastMedicalBot}{GitHub} \\[1ex]

  \textbf{Menstrual-Health-QA-Model} & \textbf{CarGoPlus} \\
  \textit{QA model for addressing menstrual health queries.} & \textit{Car rental management system with a GUI.} \\
  \textbf{Technologies:} Jupyter Notebook, Hugging Face Spaces & \textbf{Technologies:} MySQL, C++, wxWidgets \\
  \textbf{Links:} \href{https://huggingface.co/adi2606/MenstrualQA}{GitHub}, \href{https://huggingface.co/spaces/adi2606/MenstrualQA}{Demo} & \textbf{Links:} \href{https://github.com/EchoSingh/CarGoPlus}{GitHub} \\[1ex]

  \textbf{Aho-Corasick Visualization} & \textbf{ChatBot Web Project} \\
  \textit{Visualizing Aho-Corasick string-search algorithm.} & \textit{Chatbot with SQLite3-based search storage.} \\
  \textbf{Technologies:} C++, wxWidgets & \textbf{Technologies:} HTML, CSS, JavaScript, SQLite3 \\
  \textbf{Links:} \href{https://github.com/EchoSingh/AhoCorasickProject}{GitHub} & \textbf{Links:} \href{https://github.com/EchoSingh/ChatBot_WebProject}{GitHub} \\
\end{tabularx}

%----------Skills--------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textbf{Programming Languages:} & C, C++, Python, Java, SQL \\
  \textbf{Frameworks/Technologies:} & MySQL, Transformers, TensorFlow, Gradio, wxWidgets \\
  \textbf{Tools:} & Git, Jupyter Notebooks, CUDA, SQLite3 \\
  \textbf{Other:} & Model fine-tuning, AI/ML algorithms, GUI development \\
\end{tabularx}

%----------Extracurricular Activities---------
\section{Extracurricular Activities}
\begin{itemize}[leftmargin=*]
  \resumeItem{Volunteer for RFH Juniors Run 2024, organized by Rupee For Humanity (RFH), Bangalore. Links: \href{https://drive.google.com}{Drive}}
  \item Participated in multiple \textbf{Inter-college Hackathons}.
  \item Chess: Rated \textbf{2000} on Chess.com and \textbf{2200} on Lichess.org.
\end{itemize}

\end{document}
